---
title: "individual2.Rmd"
author: "Mike Brown"
date: "2/17/2021"
output: html_document
---
1.How are the ratings distributed? Create both a histogram and a boxplot and describe them. Don’t forget to mention outliers, if there are any.

```{r} 
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv")
 
hist(choco$Rating)
 boxplot(choco$Rating)
```

2.How does the number of ratings depend on the location of the company? Draw a bar chart of the number of reports.
``` {r}
y <- factor(choco$Location, levels=unique(choco$Location))
x<-table(y)
barplot(x)
```
amount of reviews seems to increase for more developed nations. more developed nations have more money for there to be more companies and potential for companies to make more than one bar. more companies and more bars within each company equates to higher amount of reviews being attributed to the respective country.

3.Do ratings depend on the cacao percentage of a chocolate bar? Create both numerical and graphical summaries, and explain. [Hint: Think about why the scatterplot is not a very good choice for visualization here.]

scatterplot is not good because there would be many duplicate values and therefore not accurate.
``` {r}
cor(choco$Cocoa_Percent, choco$Rating)
w<- choco$Rating
z<- choco$Cocoa_Percent
g<- c(w,z)
barplot(g,xlab='Rating', ylab='Cocoa Percentage')
```
correlation coefficient is very low which suggests that there is no correlation. Based on the graph above, it is clear that there is no clear indicator for whether percentage effects rating.

4. How do different bean origins compare in terms of the flavor of chocolates? Are beans from some places better than the other? Create both numerical and graphical summaries, and explain.

``` {r}
e<- (choco$Rating)
f<- choco$Bean_Origin
fac<-factor(f, levels =unique(f))
levels(fac) <- substr(levels(fac), 1, 3)
boxplot(e ~ fac, xlab='Origin', ylab='Rating')
``` 
``` {r}
head(sort(choco$Rating, decreasing = TRUE), n=900)
outstanding<- choco[choco$Rating >= 3.5,]
q<- outstanding['Bean_Origin']
as.data.frame(table(q))
```
From this table we can see that Ecuador, Peru and Venezuela have the highest amounts of observations where the rating is greater than or equal to 3.5. Their numbers are significantly higher than the rest (88, 85, 104 respectively) which leads me to believe that bean origin does have an effect on rating.

5.Brainstorm two analyses you would like to perform (with your teammates). Describe in plain language what comparisons are you making. Create suitable numerical and graphical summaries for your analyses. Describe the results.

We are going to identify a rating greater than or equal to 3.5 as outstanding/highly recommended and a rating less than or equal to 2.9 as disappointing/not recommended.
``` {r}
head(sort(choco$Rating, decreasing=FALSE), n=544)
disappointing<- choco[choco$Rating <= 2.9,]
disappointing
outstanding
length(choco$Rating)
```
Disappointing: (544/2312)100 = 23.5% of observations were disappointing
Outstanding: (875/2312)100 = 37.8% of observations were outstanding
