---
title: "individual1.Rmd"
author: "Nathan Marquardt"
date: "2/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Questions
1.How are the ratings distributed? Create both a histogram and a boxplot and describe them. Don’t forget to mention outliers, if there are any.

  Answer:
  ```{r}
  choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
  str(choco) 
  hist(choco$Rating)
  boxplot(choco$Rating)
  ```
  
  
2.How does the number of ratings depend on the location of the company? Draw a bar chart of the number of reports.

  Answer:
  ```{r}
  choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
  str(choco) 
  lvlCountry <- factor(choco$Location, levels = unique(choco$Location))
  table(lvlCountry)
  barplot(table(lvlCountry))
  ```
  
  
3.Do ratings depend on the cacao percentage of a chocolate bar? Create both numerical and graphical summaries, and explain. [Hint: Think about why the scatterplot is not a very good choice for visualization here.]

  Answer:
  ```{r}
  choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
  str(choco) 
  cor(choco$Rating, choco$Cocoa_Percent)
  x <- choco$Rating
  y <- choco$Cocoa_Percent
  plt <- c(x, y)
  barplot(plt, main="Correlation between Cocao % and Rating", xlab = 'Rating', ylab = 'Coaco Percentage')
  ```
  
  Since the correlation is closer to zero and the graph seems to be random, I would say that the cocao percentage does not correlate to the rating.
  
4.How do different bean origins compare in terms of the flavor of chocolates? Are beans from some places better than the other? Create both numerical and graphical summaries, and explain.

  Answer:
  
5.Brainstorm two analyses you would like to perform (with your teammates). Describe in plain language what comparisons are you making. Create suitable numerical and graphical summaries for your analyses. Describe the results.

  Answer:

