---
title: "individual1.Rmd"
author: "Nathan Marquardt"
date: "2/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Questions
1.How are the ratings distributed? Create both a histogram and a boxplot and describe them. Don’t forget to mention outliers, if there are any.

  Answer:
  ```{r}
  choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
  str(choco) 
  hist(choco$Rating)
  boxplot(choco$Rating)
  ```
  
  
2.How does the number of ratings depend on the location of the company? Draw a bar chart of the number of reports.

  Answer:
  ```{r}
  choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
  str(choco) 
  lvlCountry <- factor(choco$Location, levels = unique(choco$Location))
  table(lvlCountry)
  barplot(table(lvlCountry))
  ```
  
  
3.Do ratings depend on the cacao percentage of a chocolate bar? Create both numerical and graphical summaries, and explain. [Hint: Think about why the scatterplot is not a very good choice for visualization here.]

  Answer:
  ```{r}
  choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
  str(choco) 
  cor(choco$Rating, choco$Cocoa_Percent)
  x <- choco$Rating
  y <- choco$Cocoa_Percent
  plt <- c(x, y)
  barplot(plt, main="Correlation between Cocao % and Rating", xlab = 'Rating', ylab = 'Coaco Percentage')
  ```
  
  Since the correlation is closer to zero and the graph seems to be random, I would say that the cocao percentage does not correlate to the rating.
  
4.How do different bean origins compare in terms of the flavor of chocolates? Are beans from some places better than the other? Create both numerical and graphical summaries, and explain.

  Answer:
  ```{r}
  choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
  str(choco) 

  BOfct <- factor(choco$Bean_Origin)
  levels(BOfct) <- substr(levels(BOfct), 1, 3)
  boxplot(choco$Rating ~ BOfct, main = "Ratings by Bean Origin", xlab = "Bean   Origin", ylab = "Rating")
  ```
The plot above shows the boxplot of the flavor ratings by Bean Origin Countries. Most countries average in the  "Recommended" or "Disappointing" flavor category, with a few outliers in the "Highly Recommended" category. No countries' flavors averaged in the unpleasant or the Outstanding category. From this, it is hard to distinguish where a bean origin produces the best cocao. So, an idea is to take the most amount of "Outstanding" ratings per country and see what region they are located in.
  ```{r}
  chocoHRO <- choco[choco$Rating >= 4.0,] 
belize <- chocoHRO[chocoHRO$Bean_Origin == "Belize", ]
blend <- chocoHRO[chocoHRO$Bean_Origin == "Blend", ]
bolivia <- chocoHRO[chocoHRO$Bean_Origin == "Bolivia", ]
brazil <- chocoHRO[chocoHRO$Bean_Origin == "Brazil", ]
colombia <- chocoHRO[chocoHRO$Bean_Origin == "Colombia", ]
costaRica <- chocoHRO[chocoHRO$Bean_Origin == "Costa Rica", ]
ecuador <- chocoHRO[chocoHRO$Bean_Origin == "Ecuador", ]
ghana <- chocoHRO[chocoHRO$Bean_Origin == "Ghana", ]
guatemala <- chocoHRO[chocoHRO$Bean_Origin == "Guatemala", ]
haiti <- chocoHRO[chocoHRO$Bean_Origin == "Haiti", ]
indonesia <- chocoHRO[chocoHRO$Bean_Origin == "Indonesia", ]
jamaica <- chocoHRO[chocoHRO$Bean_Origin == "Jamaica", ]
madagascar <- chocoHRO[chocoHRO$Bean_Origin == "Madagascar", ]
mexico <- chocoHRO[chocoHRO$Bean_Origin == "Mexico", ]
nicaragua <- chocoHRO[chocoHRO$Bean_Origin == "Nicaragua", ]
pnewguinea <- chocoHRO[chocoHRO$Bean_Origin == "Papua New Guinea", ]
peru <- chocoHRO[chocoHRO$Bean_Origin == "Peru", ]
saotome <- chocoHRO[chocoHRO$Bean_Origin == "Sao Tome", ]
solomonislands <- chocoHRO[chocoHRO$Bean_Origin == "Solomon Islands", ]
stlucia <- chocoHRO[chocoHRO$Bean_Origin == "St. Lucia", ]
tanzania <- chocoHRO[chocoHRO$Bean_Origin == "Tanzania", ]
tobago <- chocoHRO[chocoHRO$Bean_Origin == "Tobago", ]
venezuela <- chocoHRO[chocoHRO$Bean_Origin == "Venezuela", ]
vietnam <- chocoHRO[chocoHRO$Bean_Origin == "Vietnam", ]


belizeCount <- length(belize$Rating)
blendCount <- length(blend$Rating)
boliviaCount <- length(bolivia$Rating)
brazilCount <- length(brazil$Rating)
colombiaCount <- length(colombia$Rating)
costaRicaCount <- length(costaRica$Rating)
ecuadorCount <- length(ecuador$Rating)
ghanaCount <- length(ghana$Rating)
guatemalaCount <- length(guatemala$Rating)
haitiCount <- length(haiti$Rating)
indonesiaCount <- length(indonesia$Rating)
jamaicaCount <- length(jamaica$Rating)
madagascarCount <- length(madagascar$Rating)
mexicoCount <- length(mexico$Rating)
nicaraguaCount <- length(nicaragua$Rating)
pnewguineaCount <- length(pnewguinea$Rating)
peruCount <- length(peru$Rating)
saotomeCount <- length(saotome$Rating)
solomonislandsCount <- length(solomonislands$Rating)
stluciaCount <- length(stlucia$Rating)
tanzaniaCount <- length(tanzania$Rating)
tobagoCount <- length(tobago$Rating)
venezuelaCount <- length(venezuela$Rating)
vietnamCount <- length(vietnam$Rating)

counts <- c(belizeCount, blendCount, boliviaCount, brazilCount, colombiaCount, costaRicaCount, ecuadorCount, ghanaCount, guatemalaCount, haitiCount, indonesiaCount, jamaicaCount, madagascarCount, mexicoCount, nicaraguaCount, peruCount, pnewguineaCount, saotomeCount, solomonislandsCount, stluciaCount, tanzaniaCount, tobagoCount, venezuelaCount, vietnamCount)
countryNames <- sort(unique(chocoHRO$Bean_Origin))

?barplot
barplot(counts, names.arg = substr(countryNames, 1, 3), main = "# of Outstanding Flavor Reviews by Country", xlab = "Bean Origin Countries", ylab = "# of Outstanding Flavors", col = "red")
```

  The bar plot above shows the count of "Outstanding" flavor ratings by Bean Origin Countries, which are ratings 4.0 to 5.0. Most of the countries on this list are either in South America or Africa, with the exception being Papua New Guinea. The highest count of "Outstanding" flavor ratings belongs to Venezuela.
  
5.Brainstorm two analyses you would like to perform (with your teammates). Describe in plain language what comparisons are you making. Create suitable numerical and graphical summaries for your analyses. Describe the results.

  Answer:
  ```{r}
  choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco) 

totalRatings <- length(choco$Rating)
ratingsHRO <- choco[choco$Rating >= 3.5,]
HROCount <- length(ratingsHRO$Rating)
HROPercentage <- HROCount / totalRatings
nonHROPercentage <- 1.0 - HROPercentage

slices <- c(HROPercentage, nonHROPercentage)
lbls <- c("HRO Percentage", "Other")


pie(slices, labels = lbls, main = "Pie Chart of Highly Recomended or Outstanding Ratings")
```

The analysis and pie chart above show the percentage of Highly Recommended or Outstanding flavor ratings compared to the other ratings. Around 38% of the reviews are either highly recommended or outstanding. This appears to be a little high, as the boxplot in Question 4 shows many of the averages of the reviews being in the "Recommended" Category.

```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco) 

totalRatings <- length(choco$Rating)
ratingsUD <- choco[choco$Rating <= 2.9,]
HROCount <- length(ratingsUD$Rating)
UDPercentage <- HROCount / totalRatings
nonUDPercentage <- 1.0 - UDPercentage

slices2 <- c(UDPercentage, nonUDPercentage)
lbls2 <- c("UD Percentage", "Other")


pie(slices2, labels = lbls2, main = "Pie Chart of Disappinting or Unplesant Ratings")
```

The second analysis was to to look at how many reviews received a "Disappointing" or "Unpleasant" flavor review compared to the rest of the reviews. From our analysis, we noted that around 24% of the reviews received a review in the two categories. This makes more sense as to why the the reviews averaged in the "Recommended" category, since most of the Highly "Recommended" or "Outstanding" reviews were leveled out with "Disappointing" or "Unpleasant" reviews. 
